Amazon in Presidential Speeches in Brazil: data exploration for contexts

### 2021-11-02 data_exploration_2_context.Rmd
updated stopword list

# Remove stopwords and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil"))
Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")

>>>>

# Remove stopwords and punctuation
Amazon_speeches$text <- tm::removePunctuation(Amazon_speeches$text)
Amazon_speeches$text <- tm::removeWords(Amazon_speeches$text,
                                        c(tm::stopwords("pt"), "nao", "amazonas",
                                          "amazonia", "governo", "amazonica", "ja", "aqui", "tambem",
                                          "no", "hoje", "presidente", "governador", "regiao", 
                                          "sao", "voces", "ser", "bem", "la", "so", "desta", "porque",
                                          "fazer", "quero", "ter", "vamos", "the", "of", "ha", "ai",
                                          "ate", "vai", "dizer", "estao", "it", "ver", "r", "	it",
                                          "cumprimentar", "gente", "estado", "querido", "queria",
                                          "todos", "brasil", "companheiro", "senhores", "site", 
                                          "companheiras", "companheiros", "companheira",
                                          "senhor", "senhora", "agora", "senhores", "senhoras", "caro",
                                          "grosso", "rio", "ministro", "ministra", "josé", "paulo", "pará", "acre", "roraima",
                                          "manaus", "rondônia", "ministros", "luiz", "antonio", "vou", "eduardo braga", "rio de janeiro",
                                          "sao paulo", "então", "pouco", "pode", "sul", "norte", "mato grosso", "janeiro",
                                          "outro", "onde", "discurso", "parte", "anos", "cada", "todo", "porto velho", "visite",
                                          "site secretaria", "minas gerais", "lula silva", "inácio lula", "amapa", "porto", "bahia", "é",
                                          "lá", "et", "in"))

Amazon_speeches$text <- stringr::str_remove_all(Amazon_speeches$text, " [a-z] ")
